Visualization and analysis of probability distributions of large temporal data

### 2022-02-21 Rmd/03-hakear.Rmd
response update
Juergen Q3 Chapter3 graph tickmarks and labels changed

```{r onegran-new, fig.cap="A cyclic granularity can be considered to be a categorical variable, and used to break the data into subsets. Here, side-by-side boxplots overlaid on jittered dotplots explore the distribution of of energy use by a household for two different cyclic granularities: (a) hour-of-day and (b) and month-of-year. Daily peaks occur in morning and evening hours, indicating a working household, where members leave for and return from work. More volatility of usage in summer months (Jan, Feb) is probably due to air conditioner use on just some days.", fig.pos="!b"}
```

@@

(ref:gravitas-plot-8) Comparing distribution of energy demand shown for household id 1 (a) and 7 (b) on logarithmic scale across *hod* in x-axis and *dow* in facets through quantile area plots. The value of $\wpd$ in Table 3 suggests that the harmony pair (*dow*, *hod*) is significant for household id 7, but not for id 1. This implies that distributional differences are captured more by this harmony for id 7, which is apparent from this display with more fluctuations across median and 75th percentile for different hours of the day and day of week. For id 1, patterns look similar within weekdays and weekends. Here, the median is represented by the black line, the orange area corresponds to quartile deviation and the green area corresponds to area between $10^{th}$ and $90^{th}$ quantile.

>>>>

```{r onegran-new, fig.cap="A cyclic granularity can be considered to be a categorical variable, and used to break the data into subsets. Here, side-by-side boxplots overlaid on jittered dotplots explore the distribution of energy use (on a logarithmic scale) by a household for two different cyclic granularities: (a) hour-of-day and (b) month-of-year. Daily peaks occur in morning and evening hours, indicating a working household, where members leave for and return from work. More volatility of usage in summer months in Australia (Jan, Feb) is probably due to air conditioner use on just some days.", fig.pos="!b"}
```

@@

(ref:gravitas-plot-8) Comparing distribution of energy demand shown for household id 1 (a) and 7 (b) on logarithmic scale across *hod* in x-axis and *dow* in facets through quantile area plots. The value of $\wpd$ in Table 3 suggests that the harmony pair (*dow*, *hod*) is significant for household id 7, but not for id 1. This implies that distributional differences are captured more by this harmony for id 7, which is apparent from this display with more fluctuations across median and 75th percentile for different hours of the day and day of week. For id 1, patterns look similar within different days of weekdays and weekends. Here, the median is represented by the black line, the orange area corresponds to quartile deviation and the green area corresponds to area between $10^{th}$ and $90^{th}$ quantile. The display with hod vs wdwnd would have shown higher values of wpd for id:1 (as can be verified from Table 3).
